Palmer amaranth (\emph{Amaranthus palmeri}) adaptation to agroecossystems

### 2021-07-27 Manuscript/Manuscript.Rmd
as

The field experimental unit were six adjacent 9.1 m wide (12 rows at 72.2 cm row spacing) by 10.7 m long. Each experimental unit was planted with corn or soybean, or under fallow condition. Palmer amaranth seedlings were  transplanted to the field experiment by making a whole in the soil (6 cm deep and 8 cm wide); and gently transferring to the ground (potting mix + two seedlings). After a week, one was eliminated and one was kept. There were two transplant timing: first (June 1^st^) and second (July 1^st^). There were 24 Palmer amaranth plants in each experimental unit, with a total of 144 plants. The study was repeated twice.

After transplanting, Palmer amaranth flowering was monitored until the end of the study. When a plant started flowering, the day was recorded, plant sex was identified as male or female, and plant height was measured from soil surface to the plant top. Then, aboveground plant biomass was harvest near soil surface and oven dried at 65 C until reaching constant weight before the weight of biomass (g plant^-1^) was recorded.

@@

The doy for 10, 50, and 90% Palmer amaranth cumulative flowering were determined using the *ED* function of drc package. Also, the 10, 50, and 90% Palmer amaranth cumulative flowering were compared among crop/fallow and timings using the *EDcomp* function of drc package. The EDcomp function compares the ratio of cumulative flowering using t-statistics, where P-value < 0.05 indicates that we fail to reject the null hypothesis.

Palmer amaranth height and biomass were performed with a linear mixed model using *lmer* function from "lme4" package [@bates2015]. Plant height and biomass were transformed to meet model assumption of normality . In the model, agroecosystem (crop, soybean, fallow) was the fixed effect and year nested with location the random effects. Analysis of variance was performed with *anova* function from "car" package [@fox2018]. Marginal means and compact letter display were estimated with *emmeans* and *cld* from packages "emmeans" and multcomp [@hothorn2008]

@@

```{r fig2, echo = FALSE, message=FALSE, fig.show = "hide"}
knitr::include_graphics("../data analysis/figures/combine 3.png")
```

## Palmer amaranth height and biomass {-}

@@

```{r, Figure-2, ref.label = "fig2", echo = FALSE, message = FALSE, fig.height=9, fig.width=4, fig.align='center', fig.cap='Figure caption', out.width = "150mm", out.height = "200mm"}
# You can also refer to code chunks from above to place figures at the bottom.
```

>>>>

The field experimental unit were six adjacent 9.1 m wide (12 rows at 72.2 cm row spacing) by 10.7 m long. Each experimental unit was planted with corn or soybean (DSR-1950 R2Y at 296,400 seeds ha 1), or under fallow condition. Palmer amaranth seedlings were  transplanted to the field experiment by making a whole in the soil (6 cm deep and 8 cm wide); and gently transferring to the ground (potting mix + two seedlings). After a week, one was eliminated and one was kept. There were two transplant timing: first (June 1) and second (July 1). There were 24 Palmer amaranth plants in each experimental unit, with a total of 144 plants. The study was repeated twice.

After transplanting, Palmer amaranth flowering was monitored until the end of the study. When a plant started flowering, the day was recorded, plant sex was identified as male or female, and plant height was measured from soil surface to the plant top. Then, aboveground plant biomass was harvest near soil surface and oven dried at 65 C until reaching constant weight before the weight of biomass (g plant 1) was recorded.

@@

The doy for 10, 50, and 90% Palmer amaranth cumulative flowering were determined using the *ED* function of drc package. Also, the 10, 50, and 90% Palmer amaranth cumulative flowering were compared among agroecossystems and timings using the *EDcomp* function of drc package. The EDcomp function compares the ratio of cumulative flowering using t-statistics, where P-value < 0.05 indicates that we fail to reject the null hypothesis.

Palmer amaranth height and biomass were performed with a linear mixed model using *lmer* function from "lme4" package [@bates2015]. Plant height and biomass were transformed to meet model assumption of normality. In the model, agroecosystem (crop, soybean, fallow) was the fixed effect and year nested with location the random effects. Analysis of variance was performed with *anova* function from "car" package [@fox2018]. Marginal means and compact letter display were estimated with *emmeans* and *cld* from packages "emmeans" and multcomp [@hothorn2008]

@@

```{r fig2, echo = FALSE, message=FALSE, fig.show = "hide"}
knitr::include_graphics("../data analysis/figures/Combined2.png")
```

## Height and biomass {-}

```{r fig3, echo = FALSE, message=FALSE, fig.show = "hide"}
knitr::include_graphics("../data analysis/figures/figure 3.png")
```

```{r fig4, echo = FALSE, message=FALSE, fig.show = "hide"}
knitr::include_graphics("../data analysis/figures/image.jpeg")
```

@@

```{r, Figure-2, ref.label = "fig2", echo = FALSE, message = FALSE, fig.height=9, fig.width=4, fig.align='center', fig.cap='Cumulative flowering of Palmer amaranth at first and second transplant timing (A) and day of year of 10, 50, and 90 cumulative flowering at first and second transplant timing (B)', out.width = "160mm", out.height = "130mm"}
# You can also refer to code chunks from above to place figures at the bottom.
```

```{r, Figure-3, ref.label = "fig3", echo = FALSE, message = FALSE, fig.height=9, fig.width=4, fig.align='center', fig.cap='Palmer amaranth biomass (A) and height (B) growing in corn, fallow, and soybean across Arlington, Clay Center, Grant, Lincoln, and Macomb', out.width = "130mm", out.height = "70mm"}
# You can also refer to code chunks from above to place figures at the bottom.
```

```{r, Figure-4, ref.label = "fig4", echo = FALSE, message = FALSE, fig.height=9, fig.width=4, fig.align='center', fig.cap='Harvest Palmer amaranth plants at 40 days after first transplant timing. From left to right, Palmer amaranth growing in fallow, soybean and corn in Arlington, Wisconsin', out.width = "70mm", out.height = "70mm"}
# You can also refer to code chunks from above to place figures at the bottom.
```

### 2021-07-27 Manuscript/Manuscript.tex
as

The field experimental unit were six adjacent 9.1 m wide (12 rows at
72.2 cm row spacing) by 10.7 m long. Each experimental unit was planted
with corn or soybean, or under fallow condition. Palmer amaranth
seedlings were transplanted to the field experiment by making a whole in
the soil (6 cm deep and 8 cm wide); and gently transferring to the
ground (potting mix + two seedlings). After a week, one was eliminated
and one was kept. There were two transplant timing: first (June
1\textsuperscript{st}) and second (July 1\textsuperscript{st}). There
were 24 Palmer amaranth plants in each experimental unit, with a total
of 144 plants. The study was repeated twice.

After transplanting, Palmer amaranth flowering was monitored until the
end of the study. When a plant started flowering, the day was recorded,
plant sex was identified as male or female, and plant height was
measured from soil surface to the plant top. Then, aboveground plant
biomass was harvest near soil surface and oven dried at 65 C until
reaching constant weight before the weight of biomass (g
plant\textsuperscript{-1}) was recorded.

@@

\hypertarget{palmer-amaranth-height-and-biomass}{%
\subsection*{Palmer amaranth height and
biomass}\label{palmer-amaranth-height-and-biomass}}
\addcontentsline{toc}{subsection}{Palmer amaranth height and biomass}

@@

{\centering \includegraphics[width=150mm,height=200mm]{../data analysis/figures/combine 3}

@@

\caption{Figure caption}\label{fig:Figure-2}
\end{figure}

>>>>

The field experimental unit were six adjacent 9.1 m wide (12 rows at
72.2 cm row spacing) by 10.7 m long. Each experimental unit was planted
with corn or soybean (DSR-1950 R2Y at 296,400 seeds ha 1), or under
fallow condition. Palmer amaranth seedlings were transplanted to the
field experiment by making a whole in the soil (6 cm deep and 8 cm
wide); and gently transferring to the ground (potting mix + two
seedlings). After a week, one was eliminated and one was kept. There
were two transplant timing: first (June 1) and second (July 1). There
were 24 Palmer amaranth plants in each experimental unit, with a total
of 144 plants. The study was repeated twice.

After transplanting, Palmer amaranth flowering was monitored until the
end of the study. When a plant started flowering, the day was recorded,
plant sex was identified as male or female, and plant height was
measured from soil surface to the plant top. Then, aboveground plant
biomass was harvest near soil surface and oven dried at 65 C until
reaching constant weight before the weight of biomass (g plant 1) was
recorded.

@@

\hypertarget{height-and-biomass}{%
\subsection*{Height and biomass}\label{height-and-biomass}}
\addcontentsline{toc}{subsection}{Height and biomass}

@@

{\centering \includegraphics[width=160mm,height=130mm]{../data analysis/figures/Combined2}

@@

\caption{Cumulative flowering of Palmer amaranth at first and second transplant timing (A) and day of year of 10, 50, and 90 cumulative flowering at first and second transplant timing (B)}\label{fig:Figure-2}
\end{figure}

{\centering \includegraphics[width=130mm,height=70mm]{../data analysis/figures/figure 3}

\caption{Palmer amaranth biomass (A) and height (B) growing in corn, fallow, and soybean across Arlington, Clay Center, Grant, Lincoln, and Macomb}\label{fig:Figure-3}
\end{figure}

{\centering \includegraphics[width=70mm,height=70mm]{../data analysis/figures/image}

\caption{Harvest Palmer amaranth plants at 40 days after first transplant timing. From left to right, Palmer amaranth growing in fallow, soybean and corn in Arlington, Wisconsin}\label{fig:Figure-4}
\end{figure}
